\textcolor{red}{Disambiguating Monocular Depth Estimation with a Single Transient: Supplemental Information}

### 2020-03-05 paper/eccv2020/supplement.tex

@@

We compare the output of the network $z_0$, the
median-rescaled network output (where the depth map $z_0$ is scaled pixel-wise by a
scalar $\frac{\text{median}(z_{GT})}{\text{median}(z_0)}$, $z_{GT}$ being the
ground truth depth map), the network output matched to the ground truth depth histogram, and the output of
our histogram matching method under a signal-to-background ratio (SBR) of 100.
We use the luminance of the RGB image as our reflectance map
for both SPAD simulation and histogram matching.
We show absolute difference maps and also give
the root-mean-square error (RMSE) for each example.
% \input{sections/supplement/simulation_comparison.tex}

@@

Black pixels in the ground truth depth correspond to locations where our scanner
was unable to produce an accurate depth estimate (this can occur for a variety
of reasons including dark albedo and surface specularity). These pixels are masked off and not used in the RMSE
calculation, and appear as an absolute difference of 0 in the difference maps.
% \input{sections/supplement/hardware_comparison.tex}

>>>>

\section{Comparison of diffused vs. scanned imaging}
In our experiments, we capture measurements by scanning the scene with a
single-pixel SPAD detector whose optical path is aligned with a laser. This
arrangement allows us to capture a reference ``ground truth'' depth map for
quantitative validation of our method. To emulate measurements captured using a
system where the laser and detector are diffused over the scene, we digitally
sum the measurements to obtain a single transient.

In order to verify that digital summation of scanned measurements yields results
that are similar to those captured by a diffused laser and detector, we capture
an example scene using a modified hardware prototype in both scanned and
diffused modes. The hardware prototype (shown in Fig.~\ref{fig:hardware})
consists of a more powerful laser (Katana 05HP, 532 nm) which we operate at
approximately 25 mW output power with two single-pixel SPAD detectors. One SPAD
is aligned with the optical path of the laser, and the other SPAD is operated
without a lens to integrate light from the entire scene. Both SPADs are fitted
with a 10 nm bandpass filter centered at 532 nm, which reduces the amount of
integrated ambient light. We attach a holographic diffuser (Thorlabs ED1-S50) to
the laser output in order to diffuse light onto the scene or alternatively
remove the diffuser and use a pair of scanning mirrors to scan the scene.

The modified hardware setup is used to capture an example scene in both scanned and
diffused modes, and the resulting transients are used to refine an initial depth
estimate from the Kinect RGB image. We illustrate the results of this procedure
in Fig.~\ref{fig:comparison}. The reconstructions from the scanned and diffused
measurements are similar in reconstruction quality and also show similar
quantitative improvement in terms or error over the initial depth estimate. The
normalized photon counts are also shown in Fig.~\ref{fig:comparison}, and we
note that the counts show similar trends. The number of recorded photons in
these experiments is shown in Table~\ref{tab:photon_counts}. In both cases, the
rate of detected photons is far less ($<$5\%) than the number of emitted laser
pulses, and so we conclude that the measurements are captured in the low-flux
regime where pileup effects are negligible. We attribute most of the differences
between the scanned and diffused transients to the baseline between the
positions of the diffused and scanned SPADs (see Fig.~\ref{fig:hardware}).

\begin{figure}[H]
  \centering \includegraphics[width=\textwidth]{diffused_hardware/setup.pdf}
  \caption{Modified hardware setup. The setup is used to compare scanned and
  diffused measurements and employs two SPAD detectors and two laser
  configurations. In the first configuration, the scene is illuminated by
  sending the laser light through a holographic diffuser and a lensless SPAD 
  integrates light from the entire scene. In the second, the SPAD is aligned
  with the optical path of the laser and the scene is scanned using a pair of
  scanning mirrors. The baseline between the two SPADs (right) results in some
  observed differences in the recorded transients.}
  \label{fig:dither}
\end{figure}

\begin{table}[ht!]
    \renewcommand{\arraystretch}{1.3}
    \setlength{\tabcolsep}{10pt}
     \centering
     \begin{tabular}{lccc} \toprule
         \textbf{Experiment} & \textbf{Detected Photons} & \textbf{Laser Pulses} & \textbf{Detection Rate} \\\hline
         \textbf{Scanned} & XXX & $6\times10^7$ & XXX \\
         \textbf{Diffused} & XXX & $6\times10^7$ & XXX \\
        \bottomrule
    \end{tabular}
    \vspace{0.4em}
    \caption{\textbf{Recorded photons for diffused vs. scanned scene.} In each capture mode, scanned or diffused, the number of detected photons does not exceed 5\% of the number of emitted laser pulses, placing the capture within the low-flux regime where pileup effects are negligible.}
    \label{tab:photon_counts}
\end{table}

@@

We compare the output of the network $z_0$, the
median-rescaled network output (where the depth map $z_0$ is scaled pixel-wise by a
scalar $\frac{\text{median}(z_{GT})}{\text{median}(z_0)}$, $z_{GT}$ being the
ground truth depth map), the network output matched to the ground truth depth histogram, and the output of
our histogram matching method under a signal-to-background ratio (SBR) of 100.
We use the luminance of the RGB image as our reflectance map
for both SPAD simulation and histogram matching.
We show absolute difference maps and also give
the root-mean-square error (RMSE) for each example.
\input{sections/supplement/simulation_comparison.tex}

@@

Black pixels in the ground truth depth correspond to locations where our scanner
was unable to produce an accurate depth estimate (this can occur for a variety
of reasons including dark albedo and surface specularity). These pixels are masked off and not used in the RMSE
calculation, and appear as an absolute difference of 0 in the difference maps.
 \input{sections/supplement/hardware_comparison.tex}
